My English activity log

### 2020-04-26 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
jusqu'au 26/04

author:
  - name: Aurélie Pinchart
date: 03-30-2020
preview: english.jpg
output:
  distill::distill_article:
    self_contained: false
---

@@

>>>>

author:
  - name: Aurélie Pinchart
date: 04-26-2020
preview: english.jpg
output:
  distill::distill_article:
    self_contained: false
---

@@

* **23/04/2020** :
  + I watched a video about plant metabolism https://www.youtube.com/watch?v=XSig4PR_CXs&feature=share
  + I watched a video about orchid's trap https://www.youtube.com/watch?v=_uHJGdTgtXE
  + I watched a video about orchid wasp https://www.youtube.com/watch?v=0nfgibIYbg8
  + I watched a video about nectar robbers https://www.youtube.com/watch?v=yBL_CIQD5aM

* **24/04/2020** : I watched a video about cell signaling https://www.youtube.com/watch?v=-dbRterutHY.

* **25/04/2020** : I watched a video about assumptions about marine biologists https://www.youtube.com/watch?v=hOE04I3TGL0.

* **26/04/2020** : I watched a video about a turtle which have an exposed heart https://www.youtube.com/watch?v=c3s4n8MI2u4.
